A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
fixes spelling

\subsection{Theoretical Results}
Recently, Patrascu et al. showed that simple tabulation hashing provides unexpectedly strong guarantees and is constant competitive with a truly random hash function for hashing with linear probing. In their paper, they showed that for simple tabulation hashing with linear probing if the table size is $m = (1 + \epsilon)n$, then the expected time per operation is $O(1/\epsilon^2)$. This new guarantee asymptotically matches the
bound for a truly random function. They also showed some experimental evaluations which proved that simple tabulation on fixed input length can be fast and robust when used with linear probing and cuckoo hashing.

@@

\appendix
\section{Tornado Application}
Sample Tornado 2.2.1 application used for benchmark:
 \begin{verbatim}
import tornado.httpserver
import tornado.ioloop
import tornado.wsgi

>>>>

\subsection{Theoretical Results}
Recently, P\v{a}tra\c{s}cu et al. \cite{mihai} showed that simple tabulation hashing provides unexpectedly strong guarantees and is constant competitive with a truly random hash function for hashing with linear probing. In their paper, they showed that for simple tabulation hashing with linear probing if the table size is $m = (1 + \epsilon)n$, then the expected time per operation is $O(1/\epsilon^2)$. This new guarantee asymptotically matches the
bound for a truly random function. They also showed some experimental evaluations which proved that simple tabulation on fixed input length can be fast and robust when used with linear probing and cuckoo hashing.

@@

\begin{thebibliography}{10}

\bibitem{mihai} Mihai P\v{a}tra\c{s}cu and Mikkel Thorup. The power of simple tabulation hashing. In \emph{Proc. of 43rd STOC}, 2011.

\bibitem{python} Python Software Foundation \emph{},
\texttt{http://python.org/} 2012.

\bibitem{python} Nick Welch. Hash-table-shootout. 
\texttt{https://github.com/mackstann/hash-table-shootout} 2012.

\bibitem{python} Nicholas Piël. Benchmark of Python WSGI Servers.

\texttt{http://nichol.as/benchmark-of-python-web-servers} 2010.

\end{thebibliography}
\appendix
\section{Tornado Application}
Sample Tornado 2.2.1 application used for benchmark:
 \begin{verbatim}
import tornado.httpserver
import tornado.ioloop
import tornado.wsgi
